### 2012-11-27 inst/examples/policycosts/exact_npv.Rmd

``` {r pars  }
delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 100   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.     # noise in stock assessment measurement
sigma_i <- 0.     # noise in implementation of the quota
reward <- 0       # bonus for satisfying the boundary condition
````

``` {r noise_dists }
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

@@

``` {r  SDP}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 22, length.out = 30)
````

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=16, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

>>>>

``` {r pars  }
delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.     # noise in stock assessment measurement
sigma_i <- 0.     # noise in implementation of the quota
reward <- 0       # bonus for satisfying the boundary condition
````

``` {r noise_dists }
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
````

@@

``` {r  SDP}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 10, length.out = 30)
````

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=3, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

### 2012-11-27 inst/examples/policycosts/policycosts_writeup.Rmd

``` {r setupsource}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r}
delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
reward <- 0       # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 # measurement noise, none, but part of simulation routine
z_i <- function() 1
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)             # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

```{r}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
````

@@

``` {r L2}
L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = L2(0.7586))
````

```{r fixed}
fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
    profit, delta, reward, penalty = fixed(9.103))
```

``` {r L1}
L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(1.52))
````

```{r free_increase}
free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(3.04))
````

```{r free_decrease}
free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(3.04))
````

``` {r simulate_policy}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(1.52), seed=111), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(0.7586), seed=111),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(9.103), seed=111),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(1.52), seed=111),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(1.52), seed=111)
)
````

Make data tidy (melt), fast (data.tables), and nicely labeled.

``` {r tidy}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "penalty_fn") # names are nice
````

@@

``` {r}
p0 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p0
```

```{r}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

>>>>

`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`

``` {r libraries, include=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 100              # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

```{r reed, dependson="setup"}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 10, length.out = 30)
````

## Apples to Apples levels

This can take a while, so we use explicit parallelization, 
``` {r  parallel}
require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

## Loop over penalty functions and magnitudes

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.

``` {r npv-plot, dependson="quadcosts"}
npv0 <- dat[1,3] 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

```{r apples_plot, dependson="quadcosts"}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/value), by=variable]
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

## Results

@@

``` {r L2, dependson="apples"}
L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = L2(apples["L2"]))
````

```{r fixed, dependson="apples"}
fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
    profit, delta, reward, penalty = fixed(apples["fixed"]))
```

``` {r L1, dependson="apples"}
L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(apples["L1"]))
````

```{r free_increase, dependson="apples"}
free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(apples["free_increase"]))
````

```{r free_decrease, dependson="apples"}
free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(apples["free_decrease"]))
````

We also compare to the case in which costs of harvesting increase quadratically with effort; a common approach to create smoother policies.

```{r quad_costs, dependson="apples"}
quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
```

``` {r simulate_policy, dependson=c(-1,-2,-3,-4,-5,-6)}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````

``` {r tidy, dependson="simulate_policy"}
#Make data tidy (melt), fast (data.tables), and nicely labeled.
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "penalty_fn") # names are nice
````

@@

``` {r p0, dependson="tidy"}
p0 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p0
```

```{r p1, dependson="tidy"}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r p2, dependson="tidy"}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````
